refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-08-13 paper/manuscript.tex
PAPER: add another reference
PAPER: rejigged figure

The use of specular X-ray and neutron reflectometry for the morphological characterisation of thin films on the approximate size range 10 to \SI{5000}{\angstrom} has grown remarkably over the past years \cite{Wood2017, Daillant2009}. Most neutron and X-ray sources have instruments to perform reflectometry measurements, and there is an ongoing need for accessible software programs for users of those instruments to analyse their data in a straightforward fashion, including the co-refinement of multiple contrast datasets.  Several programs are available for this purpose, with a variety of different features \cite{Nelson2006,Bjorck2007,Kienzle2011,Gerelli2016}. These programs typically create a model of the interface, and either incrementally refine the model against the data using least-squares methods, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H, Kienzle2011} to examine the posterior probability distribution of the parameters (i.e.\ the statistical variation of the parameters in a model).

@@

\begin{figure}
\centering
\label{fig:global_fit}%
\includegraphics[width=85mm]{./supporting_information/global_fit.pdf}%
%TODO: series labels on plots; delete points?;
%FIXME: not clear what you mean by the above two points.

%FIXME: artefact in high q d2o fit; truncate at Q = 0/35 - I truncated the data at 0.3.
%FIXME: h2o fit isn't great about 0.20 - tried lots of things to improve this (including patchiness), nothing seems to work

@@

%TODO add (a) and (b)
%FIXME - where should I add (a) and (b), on the graph?
\caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystal, measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red. Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.001 respectively. b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red. It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}
\end{figure}

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.pdf}
  \caption{Corner plot for the varying parameters of DMPC bilayers supported on a silicon crystal, measured at three contrasts. The sampling took $\sim$\SI{41}{\minute} on a \SI{2.8}{GHz} quad-core computer for 16 saved steps, corresponding to 4800 samples, with the steps being thinned by a factor of 500. A larger scale image is available in supporting information.}
  \label{fig:corner}
\end{figure}

>>>>

The use of specular X-ray and neutron reflectometry for the morphological characterisation of thin films on the approximate size range 10 to \SI{5000}{\angstrom} has grown remarkably over the past years \cite{Wood2017, Daillant2009}. Most neutron and X-ray sources have instruments to perform reflectometry measurements, and there is an ongoing need for accessible software programs for users of those instruments to analyse their data in a straightforward fashion, including the co-refinement of multiple contrast datasets.  Several programs are available for this purpose, with a variety of different features \cite{Nelson2006,Bjorck2007,Kienzle2011,Gerelli2016,Hughes2016}. These programs typically create a model of the interface, and either incrementally refine the model against the data using least-squares methods, or use Bayesian approaches \cite{Sivia2006, 2010arXiv1008.4686H, Kienzle2011} to examine the posterior probability distribution of the parameters (i.e.\ the statistical variation of the parameters in a model).

@@

\begin{figure}
\centering
\label{fig:global_fit}%
\includegraphics[width=85mm]{./supporting_information/global_fit.pdf}%

@@

\caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystal, measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red. Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.01 respectively. b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red. It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}
\end{figure}

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.pdf}
  \caption{Corner plot for the varying parameters of DMPC bilayers supported on a silicon crystal, measured at three contrasts. The sampling took $\sim$\SI{33}{\minute} on a \SI{2.8}{GHz} quad-core computer for 20 saved steps, corresponding to 4000 samples, with the steps being thinned by a factor of 400. A larger scale image is available in supporting information.}
  \label{fig:corner}
\end{figure}
